---
title: "R Markdown Presentation & Plotly"
author: "Abhijeet"
date: "2023-11-26"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Synopsis
This is a week 4 assignment of the Developing Data Products Course of [Data Science Specialization](https://www.coursera.org/specializations/jhu-data-science) by Johns Hopkins University on Coursera.

## Creating Plot using Plotly
1. Yahoo finance Data is used to plot stock variation which time.
2. Four stocks have been chosen, namely Apple, Amazon, Google, and Microsoft.
3. The duration of stock price variation is chosen from '2021-01-01' and to '2023-01-01'.
```{r}
suppressMessages(library(plotly))
suppressMessages(library(quantmod))
```
```{r}
symbolBasket<-c('AAPL','AMZN','GOOG','MSFT')
suppressWarnings(getSymbols(Symbols = symbolBasket,from = '2021-01-01', to = '2023-01-01'))
```
```{r}
names(AAPL)
names(AMZN)
names(GOOG)
names(MSFT)
```
# Plotting
```{r}
df <- data.frame(Date = index(AAPL), AAPL[,6],AMZN[,6],GOOG[,6], MSFT[,6])

# Create a Plotly line chart
fig<-plot_ly(df,x=~Date)
fig<-fig %>% add_lines(y = ~AAPL.Adjusted, name = "Apple")
fig <- fig %>% add_lines(y = ~AMZN.Adjusted, name = "Amazon")
fig <- fig %>% add_lines(y = ~GOOG.Adjusted, name = "Google")
fig <- fig %>% add_lines(y = ~MSFT.Adjusted, name = "Microsoft")
fig <- fig %>% layout(
  title="Stock Prices",
  xaxis = list(
    title = "Date",
    range = c('2021-01-01','2023-01-01'), 
    zeroline = F
  ),
  yaxis = list(
    title = "Price",
    range = c(0,400),
    zeroline = F,
    tickprefix = "$"
  )
) 

fig
```



